A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-19 paper/paper.tex
Add figure for semantic typing (WIP)

\section{Semantic Typing}
\label{sec:logreldep}

>>>>

\section{Semantic Typing}
\label{sec:logreldep}
\begin{figure}[h]
  \begin{equation*}
    \begin{split}
      [ [[Bool]] ]_i &= \{ [[a]] \mid [[a =>+ true]] \text{ or } [[a =>+ false]] \} \\
      [ [[Void]] ]_i &= \emptyset \\
      [ [[a ~ b : A]] ]_i &= \{ [[p]] \mid [[p =>+ refl]] \text { and } [[a<=>b]] \}\\
    \end{split}
  \end{equation*}
  \caption{Logical relation for \lang}
  \label{fig:logrel}
\end{figure}

In this section, we show the definition of the logical relation as a
partial function in Figure~\ref{fig:logrel}. The logical relation can
be viewed as a partial function that takes a closed type,
a natural number $[[i]]$ representing the universe level, and
returns a set of closed terms that \emph{semantically} inhabit the
closed type, though we do not strictly enforce the closedness of
either the type or the term.
